Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-27 mu/article/article.tex
sab
Finishing final description for alt structure

150$^{\circ}$ is the zone of the maximum response for both,

@@

polarization angle is $\alpha = 145^{\circ}$. In the top frames of Figs.
\ref{fig:alt-vx-comp-rtp}  and \ref{fig:alt-vy-comp-rtp} we present the results
for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the photon
energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles.
Also in the bottom frames of Figs. \ref{fig:alt-vx-comp-rtp} and 

@@

@@

@@

$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $145^{\circ}$.

@@

see that for the energy range from 0.70\,eV to 0.75\,eV all the $xx$, $xy$, and
$xz$ components contribute with almost the same intensity giving a total spin-
velocity of 19.3\,Km/s and spin polar and azimuthal angles $\varphi =
45.8^{\circ}$ and $\theta=40.7^{\circ}$.

@@

In the other hand, for the energy range from 0.88\,eV to 0.95\,eV there is a
major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$ component
resulting in a spin-velocity magnitude of 30.9\,Km/s being this magnitude the
most intense for $|\mathcal{V}^{\mathrm{x}}|$. In this case the polar angle is
$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is
$\theta=290.4^{\circ}$.

@@

Also there is another zone of interest for energies from 0.70\,eV to 0.75\,eV
and same polarization angles range where a local maximum is obtained. From Figs.
\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
respectively.

@@

Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.

@@

\ref{fig:alt-vy-comp-rtp} we have that for the energy range from 0.70\,eV to
0.74\,eV the $yz$ component have a more intense response than $yx$ and $yy$
components and they give a total spin-velocity of 51.9\,Km/s and result in polar
angle $\varphi=140.7^{\circ}$ and spin azimuthal angle of
$\theta=221.5^{\circ}$.

@@

For the energy range from 0.88\,eV to 0.95\,eV all three components have similar
intensities resulting in a spin-velocity magnitude of
$|\mathcal{V}^{\mathrm{y}}| =$ 52.3\,Km/s being this response 1.7 times mores
intense than the most intense response of $|\mathcal{V}^{\mathrm{x}}|$. The
corresponding polar and azimuthal angles for $|\mathcal{V}^{\mathrm{y}}|$ in
this energy range are $\theta = 129.0 ^{\circ}$ and $\varphi = 228.9 ^{\circ}$.

@@

Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.60\,eV to 1.0\,eV \textcolor{red}{keeping
the same spin polarization for all this range.} 

@@

\begin{figure}[tb]
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-lay}]
    {\includegraphics[width=\linewidth]{figures/blank}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-lay}]
    {\includegraphics[width=\linewidth]{figures/blank}}
    \caption{Layer-by-layer contribution of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ for a polarization angle $\alpha=145^{\circ}$
    for the \emph{alt} structure.}
    \label{fig:alt-vab-lay}
\begin{figure}[tb]
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{alt} structure.}
    \label{fig:alt-vyz-lay}

% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{ab}|
% %% files: 
% %%%%%%%%%%%%%%%%
In Fig. \ref{fig:alt-vab-lay} we show the layer-by-layer contribution of
$|\mathcal{V}^{\mathrm{ab}}|$  for the \emph{alt} structure. The corresponding
layer division and atom types and positions are presented in Table 
% 
\ref{tab:alt-unitcell} and depicted in Fig. \ref{fig:alt-struc}. In the layer-
by-layer contribution for $|\mathcal{V}^{\mathrm{x}}|$ (Fig. \ref{fig:alt-vx-lay})
we have that
% 
\textcolor{red}{\ldots}
% 
Also, for the layer-by-layer contribution for $|\mathcal{V}^{\mathrm{y}}|$ (Fig.
\ref{fig:alt-vy-lay}) we have that
% 
\textcolor{red}{\ldots}
%
% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
% %%%%%%%%%%%%%%%%
From the bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
the \emph{alt} structure the most intense component of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an
energy incident beam of 0.72\,eV. This component and the corresponding layer by
layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
in the same direction resulting in a total response
$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
0.912\,eV.

@@

polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is 0.088\,eV. 

@@

bottom frame of Fig. \ref{fig:up-vx-comp- rtp-2} we have the three components

>>>>

150$^{\circ}$ is the zone where the maximum response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.

@@

energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
145^{\circ}$. In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 

@@

\ref{fig:alt-vy-comp-rtp} we present the results for
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)fixing
the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the
photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (left scale). Also in the bottom frames of Figs. 
\ref{fig:alt-vx-comp-rtp} and

@@

$|\mathcal{V}^{\mathrm{x}}|$ and 
$|\mathcal{V}^{\mathrm{y}}|$ 
in the corresponding components
$\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,

@@

$\mathcal{V}^{\mathrm{yx}}$,
$\mathcal{V}^{\mathrm{yy}}$
$\mathcal{V}^{\mathrm{yz}}$ 
with $\alpha$ fixed to $145^{\circ}$.

@@

see that for an incoming beam energy of 0.720\,eV the components contributions 
are similar having values of

@@

$\mathcal{V}^{\mathrm{xx}}= 10.5$\,Km/s, 
$\mathcal{V}^{\mathrm{xy}}=  9.1$\,Km/s, and
$\mathcal{V}^{\mathrm{xz}}= 13.5$\,Km/s

@@

resulting in a total spin-velocity 

@@

$|\mathcal{V}^{\mathrm{x}}|=19.4$\,Km/s 
and spin polar and azimuthal angles $\varphi = 45.8^{\circ}$ and
$\theta=40.7^{\circ}$, respectively.
In the other hand, for an energy of the incoming beam equal to 0.912\,eV
we found that the contribution of the components are 
$\mathcal{V}^{\mathrm{xx}}=   4.8$\,Km/s
$\mathcal{V}^{\mathrm{xy}}= -12.8$\,Km/s, and 
$\mathcal{V}^{\mathrm{xz}}= -27.7$\,Km/s
having a mayor response coming from the $xz$ component and resulting in a spin-
velocity magnitude $|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s being this the
absolute maximum fixing the spin-velocity in the $x$ direction. Then, the
components give us polar and azimuthal angles with values of
$\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
variation with the incoming energy beam are presented in the right scale of the
top frame of Fig \ref{fig:alt-vx-comp-rtp}.
Finally we have that since the onset of the response till an energy of the
incoming bean of 0.744\,eV the three components of $|\mathcal{V}^{\mathrm{x}}|$
are positive while for the range from 0.746\,eV to 0.886\,eV the
$\mathcal{V}^{\mathrm{xx}}$ component is positive but the
$\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
direction. This is due to a change in the spin polarization direction. Finally after the enrgy value of 0.886\,eV the response decreases and goes to zero. 

@@

\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV the $yz$ component have a major contribution than the $yx$ and $yy$ components having values of 

@@

$\mathcal{V}^{\mathrm{yx}}= -24.6$\,Km/s, 
$\mathcal{V}^{\mathrm{yy}}= -21.8$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s

@@

resulting in a total spin-velocity

@@

$|\mathcal{V}^{\mathrm{y}}|=51.9$\,Km/s
and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and $\theta=221.6^{\circ}$, respectively.
Also, for an energy of the incoming beam of 0.912\,eV we found that the contribution of the components are 
$\mathcal{V}^{\mathrm{xx}}=-26.7$\,Km/s
$\mathcal{V}^{\mathrm{xy}}=-30.6$\,Km/s, and
$\mathcal{V}^{\mathrm{xz}}=-32.9$\,Km/s
having all the three components similar contributions and resulting in a spin-
velocity magnitude $|\mathcal{V}^{\mathrm{y}}|=52.3$\,Km/s being this the
absolute maximum spin-velocity for the velocity fixed to the $y$ direction and
being 1.7 times more intense than the maximum of $|\mathcal{V}^{\mathrm{x}}|$.
The components then give us the polar and azimuthal angles with values of
$\varphi=129.0^{\circ}$ and $\theta=228.9^{\circ}$, respectively. This angles
and the corresponding variation is presented in the right sale of the top frame
of Fig. \ref{fig:alt-vy-comp-rtp}.
We also have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative keeping the same spin polarization since the onset of the response to a
energy of the incoming beam of 0.886\,eV when the response decreases and goes to
zero.
% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
the \emph{alt} structure the most intense component of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an
energy incident beam of 0.72\,eV. This component and the corresponding layer by
layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
in the same direction resulting in a total response
$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
0.912\,eV.

@@

polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.

@@

bottom frame of Fig. \ref{fig:up-vx-comp-rtp-2} we have the three components
